resistanceModelNotesAndy

### 2015-03-23 resistanceModelNotesAndy.Rmd
progress notes

Insecticide coverage for females: 0.1, 0.2, 0.6, 0.8, 0.9 (n=5) **9 & 15**  
Insecticide coverage for males: as for females, or half that of females (n=2) **18 & 24**  
‘New’ insecticide resistance starting freq: 0.0001, 0.001, 0.01 (n=3) **6**  
‘Old’ insecticide resistance starting freq: 0.05, 0.1, 0.2, 0.5, 0.8 (n=5) **7**  
Resistance heterozygous fitness: 0.5, 0.75. 1    (n=3 for each insecticide) **?28 & 30**  
Sensitive heterozygous fitness:0, 0.2, 0.4 (n=3 for each insecticide) **?27 & 29**  
Resistance allele dominance: 0, 0.2, 0.5, 0.9, 1 for each locus (n=5 for each locus) **35,38 do to start**  
Fitness costs: 0, 0.05, 0.1 (n=3) **43&44**  
Fitness dominance: 0, 0.5, 1 (n=3) **33&36**

@@

```{r}
resistanceMaster(params.csv = FALSE)
```

@@

**19/3/15** sat 10.15-2.15 4hrs

@@

@@

@@

1. create setInputOneScenario to enable setting inputs for a single scenario
+ sensible defaults
+ later will allow customised scenarios e.g. setInputCurtisFig1
+ will reduce code volume and repetition in createInputMatrix

@@

1. sort that resistSimple will only work with calibration of 1012

1. make it easier to run a single scenario and default scenarios
+ might do this by first adding a function rather than changing existing stuff
1. i think the main visual output is the frequency of resistance over time
1. start creating a vignette to help me understand how the model works

>>>>

Insecticide coverage for females: 0.1, 0.2, 0.6, 0.8, 0.9 (n=5) **9 & 15**  
Insecticide coverage for males: as for females, or half that of females (n=2) **18 & 24**  
‘New’ insecticide resistance starting freq: 0.0001, 0.001, 0.01 (n=3) **6**  
‘Old’ insecticide resistance starting freq: 0.05, 0.1, 0.2, 0.5, 0.8 (n=5) **7**  
Resistance heterozygous fitness: 0.5, 0.75. 1    (n=3 for each insecticide) **?28 & 30**  
Sensitive heterozygous fitness:0, 0.2, 0.4 (n=3 for each insecticide) **?27 & 29**  
Resistance allele dominance: 0, 0.2, 0.5, 0.9, 1 for each locus (n=5 for each locus) **32, 35 do to start**  
Fitness costs: 0, 0.05, 0.1 (n=3) **43&44**  
Fitness dominance: 0, 0.5, 1 (n=3) **33&36**

@@

```{r}
require(devtools)    
install_github('AndySouth/resistance') 
library(resistance)
resistanceMaster(params.csv = FALSE)
```

@@

**19/3/15** sat 10.15

@@

Created setInputOneScenario to enable setting inputs for a single scenario
+ sensible defaults
+ later will allow customised scenarios e.g. setInputCurtisFig1
+ will reduce code volume and repetition in createInputMatrix

@@

**22/3/15** mon 9.45-11.45 2hrs 5-6

created a modified plot allele freq function to be able to see overlapping lines

Default settings :
```{r}
resistSimple()
```

Reducing dominance coefficient of locus1 from 1 shifts curves to right & separates locus 1 & 2
```{r}
resistSimple(h.RS1_A0=0.17)
```

But then setting dominance coefficient of locus2 to anything less than 0.7 grounds the curves (actually by pushing them further to right).
```{r}
resistSimple(h.RS1_A0=0.17,h.RS2_0B=0.7)
```

Reducing the selection coefficient for locus1 in A (from 1) pushes curves to right, but strangely doesn't separate locus 1 & 2 ??
```{r}
resistSimple(s.RR1_A0=0.17)
```

Put variable names into the suggested sensitivity analysis table.

Thinking about creating a shiny app(s) within the resistance package.
[Advice from RStudio](http://rstudio.github.io/shiny/tutorial/#deployment-local)

Put your Shiny application directory under the package’s inst directory, then create and export a function that contains something like this:

`shiny::runApp(system.file('appdir', package='packagename'))`

I might be able to use something like [this](http://shiny.rstudio.com/gallery/plot-plus-three-columns.html) to put inputs in columns.

Or perhaps better to keep it to a single column to start ?

Starting frequency of resistance
Locus1
Locus2

Exposure to insecticide (same for M&F & in Curtis for both insecticides)

Fitness of susceptibles in presence of insecticide.
Insecticide1
Insecticide2

Dominance of resistance
Locus1
Locus2

Selective advantage of resistance
Locus1
Locus2

It could perhaps be 2 columns, Locus1 & Locus2

Or to fit better with widget titles, 2 rows (l1&2) with 5 columns.

@@

1. look at modifying other parameters

1. start creating a shinyapp and/or vignette to help me understand how the model works

@@

1. make it easier to run a single scenario and default scenarios
+ might do this by first adding a function rather than changing existing stuff
1. i think the main visual output is the frequency of resistance over time
